{\LARGE {\color{red}PLACEHOLDER-TITLE:} Functional Linear Regression in a Scalar-on-Function Setting with Applications to Near-Infrared Spectroscopy}

### 2022-01-16 main.tex
update
Added fancy equation to main document

\begin{document}
	\title{{\LARGE {\color{red}PLACEHOLDER-TITLE:} Functional Linear Regression in a Scalar-on-Function Setting with Applications to SOMETHING}}
	\author{Jonghun Baek, Jakob Juergens, Jonathan Willnow}
	\date{{\color{red}whenever}}
	\maketitle
	\vspace{1.5 cm}
	\begin{center}
		Research Module in Econometrics and Statistics \\
		Winter Semester 2021/2022
	\end{center}

@@

	\begin{equation}
		\begin{split}
			Y(\omega) & = \alpha + \int_{0}^{1}\left[\left(\sum_{j = 1}^{\infty} \psi_j  b_j(s)\right) F(\omega)(s) \right]\mathrm{d}s + \epsilon(\omega) \\
			& = \alpha + \sum_{j = 1}^{\infty} \left[\psi_j \textcolor{red}{\int_{0}^{1} F(\omega)(s) b_j(s)\mathrm{d}s}\right] + \epsilon(\omega) \\
			& = \alpha + \sum_{j = 1}^{\infty} \psi_j \textcolor{red}{\langle F(\omega), b_j \rangle} + \epsilon(\omega) 
			  = \alpha + \sum_{j = 1}^{\infty} \psi_j \textcolor{red}{Z_j(\omega)} + \epsilon(\omega)
		\end{split}
	\end{equation}

@@

@@

		\begin{itemize}
			\item $\tilde{\xi}_{j} \sim \mathcal{N}(0,\hat{\lambda}_j)$ and $\tilde{\xi}_{j} \independent \tilde{\xi}_{k}$ for $j \neq k$
			\item Simplification: the $\xi_{j}$ do not follow a normal
			\item $\tilde{X}(\omega)(t)$, $\hat{\mu}(t)$ and $\hat{\nu}_j(t)$ are approximated as vectors in $\mathbb{R}^{401}$.
		\end{itemize}

@@

>>>>

\begin{document}
	\title{{\LARGE {\color{red}PLACEHOLDER-TITLE:} Functional Linear Regression in a Scalar-on-Function Setting with Applications to Near-Infrared Spectroscopy}}
	\author{Jonghun Baek, Jakob Juergens, Jonathan Willnow}
	\date{11.02.2022}
	\maketitle
	\vspace{1.5 cm}
	\begin{center}
		Research Module in Econometrics and Statistics \\
		Winter Semester 2021/2022
	\end{center}

@@

	\begin{equation}
		\begin{split}
			Y(\omega) & = \alpha + \int_{0}^{1} {\color{blue}\beta(s)} X(\omega)(s)\mathrm{d}s + \epsilon(\omega) \\
			& = \alpha + \int_{0}^{1}\left[{\color{blue}\left(\sum_{j \in \mathcal{I}} c_j \phi_j(s)\right)} X(\omega)(s) \right]\mathrm{d}s + \epsilon(\omega) \\
			& = \alpha + \sum_{j \in \mathcal{I}} \left[c_j \textcolor{red}{\int_{0}^{1} X(\omega)(s) \phi_j(s)\mathrm{d}s}\right] + \epsilon(\omega) \\
			& = \alpha + \sum_{j \in \mathcal{I}} c_j \textcolor{red}{\langle X(\omega), \phi_j \rangle} + \epsilon(\omega) 
		      = \alpha + \sum_{j \in \mathcal{I}} c_j \textcolor{red}{Z_j(\omega)} + \epsilon(\omega)
		\end{split}
	\end{equation}

@@

	{\color{red} This fancy equation will be very useful to explain our simulation.}

	\begin{equation}
		\begin{split}
			Y(\omega) & = \alpha + \int_{0}^{1} {\color{blue}\beta(s)} {\color{red}X(\omega)(s)}\mathrm{d}s + \epsilon(\omega) \\
			& = \alpha + \int_{0}^{1}\left[{\color{blue}\left(\sum_{j \in \mathcal{I}} c_j  \phi_j(s)\right)} {\color{red}\left(\sum_{k \in \mathcal{L}} d_k(\omega)  \psi_k(s)\right)} \right]\mathrm{d}s + \epsilon(\omega) \\
			& = \alpha + \sum_{j \in \mathcal{I}} \left[ c_j \sum_{k \in \mathcal{L}} \textcolor{teal}{d_k(\omega) \int_{0}^{1} \phi_j(s) \psi_k(s) \mathrm{d}s}\right] + \epsilon(\omega)
			= \alpha + \sum_{j \in \mathcal{I}} \left[c_j \sum_{k \in \mathcal{L}}  \textcolor{teal}{Z_{j, k}(\omega)} \right] + \epsilon(\omega) \\
			& \approx \alpha + \sum_{j = 1}^{J} \left[c_j \textcolor{violet}{\sum_{k = 1}^{K}  Z_{j, k}(\omega)} \right] + \epsilon(\omega)
			= \alpha + \sum_{j = 1}^{J} \left[c_j \textcolor{violet}{\tilde{Z}_{j}(\omega)} \right] + \epsilon(\omega)	
		\end{split}
	\end{equation}

@@

		\begin{itemize}
			\item $\tilde{\xi}_{j} \sim \mathcal{N}(0,\hat{\lambda}_j)$ and $\tilde{\xi}_{j}\independent \tilde{\xi}_{k}$ for $j \neq k$
			\item Simplification: the $\xi_{j}$ do not follow a normal
			\item $\tilde{X}(\omega)(t)$, $\hat{\mu}(t)$ and $\hat{\nu}_j(t)$ are approximated as vectors in $\mathbb{R}^{401}$.
		\end{itemize}

@@

	\subsection{Put in appendix - Simulation setup cont.}

	The
